---
title: "Bioinformatics Analysis Tutorial 2024"
format: html
---

# Introduction

This tutorial demonstrates a basic bioinformatics analysis pipeline using the PBMC 68k dataset. We will cover quality control, normalization, dimensionality reduction, and UMAP projections.

# Setup

First, load the necessary libraries and the dataset.

```{r}
library(Seurat)
library(dplyr)
library(ggplot2)

# Load the PBMC dataset
pbmc.data <- Read10X(data.dir = "path/to/your/data/")
```

Quality Control
Filter out cells with extreme counts.

```{r}
pbmc <- CreateSeuratObject(counts = pbmc.data, project = "pbmc68k", min.cells = 3, min.features = 200)
pbmc <- subset(pbmc, subset = nFeature_RNA > 200 & nFeature_RNA < 2500 & percent.mt < 5)
```

Normalization
Normalize the data to make downstream analysis more robust.

```{r}
pbmc <- NormalizeData(pbmc, normalization.method = "LogNormalize", scale.factor = 10000)
```


Dimensionality Reduction
Perform PCA on the normalized data.

```{r}
pbmc <- FindVariableFeatures(pbmc, selection.method = "vst", nfeatures = 2000)
pbmc <- ScaleData(pbmc, features = rownames(pbmc))
pbmc <- RunPCA(pbmc, features = VariableFeatures(object = pbmc))
```

UMAP Projections
Visualize the data in two dimensions using UMAP.

```{r}
pbmc <- RunUMAP(pbmc, dims = 1:10)
DimPlot(pbmc, reduction = "umap")
```

Conclusion
This tutorial provided a brief overview of conducting a bioinformatics analysis with the PBMC 68k dataset. The steps included quality control, normalization, dimensionality reduction, and visualization with UMAP.

```
